InteroceptionStudy_GPValidation

### 2021-08-20 Experiment 2.Rmd
Update Experiment 2.Rmd

subset(tmp.df3, tNo == 10)%>%
  group_by(ssid, tNo)%>%
  mutate(pupil_z = pup_interp_mad - mean(pup_interp_mad))%>%
ggplot(aes(x = timerezero3, y= pupil_z))+
    # geom_smooth(se = F)+
  geom_smooth()+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)+
  xlim(-6,15)
```
unique(tmp.df3$ssid)

```{r}
ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= pup_basCor, colour = as.factor(ssid)))+
    geom_smooth(se = T)+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

tmp.df3<- tmp.df3%>%
  arrange(ssid,tNo, time)

>>>>

# preparation
subset(tmp.df3, tNo == 10)%>%
  group_by(ssid, tNo)%>%
  mutate(pupil_z = pup_interp_mad - mean(pup_interp_mad, na.rm = TRUE))%>%
  ungroup()%>%
ggplot(aes(x = timerezero3, y= pupil_z))+
    # geom_smooth(se = F)+
  stat_summary(fun = mean, geom = 'line')+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)+
  xlim(-3,15)
```
unique(tmp.df3$ssid)

```{r}
# rest period
ggplot(subset(tmp.df3, tmp.df3$Condition == 'Rest') , aes(x = timerezero3, y= pup_basCor, colour = as.factor(ssid)))+
    geom_smooth(se = T)+
    geom_vline(aes(xintercept = 0), colour = 'red', linetype = 'dashed', size = 2)+
    geom_vline(aes(xintercept = 4), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 8), colour = 'gray30', linetype = 'dotted', size = 2)+
    geom_vline(aes(xintercept = 6), colour = 'blue', linetype = 'dashed', size = 2)

@@

tmp.df3<- tmp.df3%>%
  arrange(ssid, time,tNo)
